% Chapter Template

\chapter{Project Requirements} % Main chapter title

\label{Chapter2} % Change X to a consecutive number; for referencing this chapter elsewhere, use \ref{ChapterX}

\lhead{Chapter 2. \emph{Project Requirements}} % Change X to a consecutive number; this is for the header on each page - perhaps a shortened title


\section{Functional Requirements}


\subsection{WebRTC}

\begin{itemize}
    \item Enable real-time delivery of graphics streams on the web.
    \item Support secure and efficient streaming of graphics data.
    \item Ensure compatibility with modern web browsers and platforms.
\end{itemize}


\subsection{WebGPU}

\begin{itemize}
    \item Develop a native component for real-time graphics rendering on the server using WebGPU.
    \item Support efficient and optimized graphics rendering techniques.
    \item Handle shader languages such as GLSL or SPIR-V.
\end{itemize}


\subsection{DevSync}

\begin{itemize}
    \item Enable real-time code editing, compilation, and hot reloading of the graphics viewport.
    \item Support a seamless development experience for developers working on graphics payloads.
    \item Integrate development tools and frameworks that facilitate live code updates and hot module replacement.
\end{itemize}


\subsection{Compiler Infrastructure}

\begin{itemize}
    \item Implement remote caching of compiled resources to reduce the turnaround time for graphics compilation.
    \item Utilize distributed caching systems or cloud-based storage solutions for storing compiled resources.
    \item Optimize resource management and ensure efficient compilation processes.
\end{itemize}


\subsection{Collaboration and Coherence}

\begin{itemize}
    \item Enable collaboration among developers and researchers working on the project.
    \item Utilize version control systems (e.g., Git) and project management tools (e.g., GitHub, Jira) for effective collaboration.
    \item Foster a coherent and collaborative end-to-end developer experience.
\end{itemize}


\subsection{Open Source}

\begin{itemize}
    \item Follow open-source development practices and guidelines.
    \item Enable easy contribution from the community.
    \item Comply with open-source licenses and requirements.
\end{itemize}


\subsection{Cloud Infrastructure}

\begin{itemize}
    \item Enable deployment of the remote access system using cloud-based infrastructure and services.
    \item Manage GPU resources efficiently within the cloud environment.
    \item Ensure scalability, reliability, and security of the cloud infrastructure.
\end{itemize}


\subsection{Security}

\begin{itemize}
    \item Employ authentication and authorization mechanisms to control user access.
    \item Ensure secure remote access to the GPU-based applications.
    \item Protect sensitive data and prevent unauthorized access or data breaches.
\end{itemize}


\subsection{Documentation and Testing}

\begin{itemize}
    \item Provide clear and comprehensive documentation for developers and users.
    \item Utilize testing frameworks and methodologies to ensure the reliability and quality of the applications.
\end{itemize}


\section{Non-Functional Requirements}


\subsection{Performance}

\begin{itemize}
    \item Provide real-time graphics rendering and streaming with minimal latency.
    \item Optimize resource utilization for efficient compilation and caching processes.
    \item Support a scalable infrastructure to handle multiple concurrent users.
\end{itemize}


\subsection{Usability}

\begin{itemize}
    \item Offer an intuitive and user-friendly interface for developers and researchers.
    \item Provide clear instructions and documentation for setup, configuration, and usage.
    \item Support seamless integration with popular development environments and tools.
\end{itemize}


\subsection{Reliability}

\begin{itemize}
    \item Ensure high availability and uptime of the remote access system.
    \item Implement error handling and recovery mechanisms to handle exceptions and failures.
    \item Regularly monitor and maintain system stability and performance.
\end{itemize}


\subsection{Security}

\begin{itemize}
    \item Implement robust security measures to protect user data and prevent unauthorized access.
    \item Follow security best practices and industry standards.
    \item Regularly update and patch the system to address security vulnerabilities.
\end{itemize}


\subsection{Scalability}

\begin{itemize}
    \item Support a growing user base and increasing demands for GPU resources.
    \item Scale the infrastructure seamlessly to handle additional users and workloads.
    \item Optimize resource allocation and management for scalability.
\end{itemize}

\subsection{Compatibility}

\begin{itemize}
    \item Support major web browsers and platforms for web-based delivery of graphics streams.
    \item Integrate with popular development tools and frameworks for code editing and compilation.
    \item Ensure compatibility with various operating systems and hardware configurations.
\end{itemize}